Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-04 Manuscript/manuscript.tex
Changed eps figures in manuscript to pdf

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.eps}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: Chemical structure of POPC with definitions of different order parameters calculated.
    Middle: Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.
    Bottom: X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    } 
  \todo{X-label misses glycerol region. JOE: glycerol belongs to the headgroup part, but, yes, it wouldn't hurt to write it explicitly. SAMULI: I would maybe remove the whole text, tell the information in caption and increase the order parameter figure size in z-direction.} \\
  \todo{Also acyl chain points should correspond the legends and maybe have the same size as HG and glycerol.} \\
  \todo{Legends would be more clear without multiple points.}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.eps}
  \caption{\label{OrderParameterCHANGESsurf}
    Headgroup order parameter changes and P-N vector orientation as a function of
    cationic surfactant (dihexadecyldimethylammonium bromide, 2C$_{16}$$^+$N2C$_1$Br$^-$)
    in PC bilayer from simulations and experiments \cite{scherer89}.
  }
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: Chemical structure of POPC with definitions of different order parameters calculated.
    Middle: Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.
    Bottom: X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    } 
  \todo{X-label misses glycerol region. JOE: glycerol belongs to the headgroup part, but, yes, it wouldn't hurt to write it explicitly. SAMULI: I would maybe remove the whole text, tell the information in caption and increase the order parameter figure size in z-direction.} \\
  \todo{Also acyl chain points should correspond the legends and maybe have the same size as HG and glycerol.} \\
  \todo{Legends would be more clear without multiple points.}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.pdf}
  \caption{\label{OrderParameterCHANGESsurf}
    Headgroup order parameter changes and P-N vector orientation as a function of
    cationic surfactant (dihexadecyldimethylammonium bromide, 2C$_{16}$$^+$N2C$_1$Br$^-$)
    in PC bilayer from simulations and experiments \cite{scherer89}.
  }
\end{figure}
